---
title: "PCA of EVI attributes of Q. pyreanica"
author: "AJ Perez-Luque (@ajpelu)"
date: "2016 March"
output:  
  md_document:
    variant: markdown_github
---
  
## Read data 
  
```{r wd, echo=FALSE}
#---------------------------------
# Set working directory 
# machine <- "/Users/ajpelu"
machine <- "/Users/ajpeluLap"

di <- paste(machine, "/Dropbox/MS/MS_QUERCUS_ENVIRON/5_REANALYSIS/qpyr_efts", sep = "")
#---------------------------------
```

```{r packages, warning=FALSE}
library("dplyr")
library("lubridate")
```

```{r}
# Read data
evi <- read.csv(file=paste(di, "/data/evi_attributes_all.csv", sep= ""), header = TRUE, sep = ',')
rawdata <- read.csv(file=paste(di, "/data/raw_iv.csv", sep= ""), header = TRUE, sep = ',')
```

```{r}
# Prepare data
## For dates we used a julian day approach (with lubridate)
evi <- evi %>% 
  mutate(jd_min = lubridate::yday(as.Date(date_min)),
         jd_max = lubridate::yday(as.Date(date_max)))



## Convert to hydrological day
# What is the julian day of the 01-Oct for the period  
aux <- numeric()
years <- seq(2000, 2013, 1)
for (i in years){
x <- lubridate::yday(as.Date(paste(i,"-10-01", sep="")))
aux <- c(aux, x)
} 

star_hyear <- median(aux)
star_hyear

# we consider 366 
# Create two variables with hydrological dates
evi <- evi %>% 
  mutate(hd_min = ifelse(jd_min > 273, jd_min - 273, jd_min + 92),
         hd_max = ifelse(jd_max > 273, jd_max - 273, jd_max + 92))

# Get coordinates and pob 
evi_aux <- rawdata %>% select(iv_malla_modi_id, lng, lat, poblacion) %>%
  group_by(iv_malla_modi_id) %>% unique()


# Join dataframes 
evi <- evi %>% inner_join(evi_aux, by="iv_malla_modi_id") 

```

# PCA
```{r}
# Get 
# Select variables and mean value
df_pca_evi <- evi %>% 
  select(iv_malla_modi_id, poblacion, evi_mean, evi_min, evi_max, jd_min, jd_max, evi_cv) %>%
  group_by(iv_malla_modi_id) %>%
  summarise_each(funs(mean(.))) %>% 
  filter(poblacion != 9) %>% 
  mutate(pop_group=ifelse(poblacion < 2, 'A', 
                          ifelse(poblacion < 6, 'B', 'C')))


df_pca_evi <- as.data.frame(df_pca_evi[c(9,1:8)])


# PCA evi 
pca_evi <- prcomp(df_pca_evi[,-c(1:3)], scale=TRUE)

# Eigenvalues 
# Los eigenvalues es sd^2 
ev <- (pca_evi$sdev)^2


# Obtener tabla de importancia de los ejes
summary(pca_evi)


## 
# Plot 
colores <- c("black", "red", "green3", "blue","cyan", "magenta", "yellow", "gray")
library("pca3d")
pca3d(pca_evi, group = df_pca_evi[,"poblacion"], 
      palette =colores, show.ellipses=TRUE,
      ellipse.ci=0.75, show.plane=TRUE)

pca2d(pca_evi, group = df_pca_evi[,"poblacion"], components = c(1,2),
      show.ellipses=TRUE, ellipse.ci=0.75, palette =colores)

, show.ellipses=TRUE,
      ellipse.ci=0.75, show.plane=TRUE)



library(MASS)
df <- df_pca_evi[,c(3:9)]
lda.evi <- lda(as.factor(poblacion)~.,data=df)


# Valores predichos
prelda <- predict(lda.evi, dim=3)

# Creo un dataframe con puntuaciones en cada LDA y poblaciones 
pp.evi <- as.data.frame(cbind(prelda$x, prelda$class))
names(pp.evi) <- c('lda1','lda2','lda3','pop')




# lattice 
library(lattice)
trellis.device(pdf, file=paste(di, '/3_LDA/LDA_3d.pdf', sep=''), width=6, height=6) 
ldaplot3d <- cloud(lda2~lda1*lda3, groups=pop, data=pp.evi, pch=19, 
                   screen=list(z=-40,x=-70,y=25), 
                   scales = list(arrows = FALSE),
                   alpha=.5, auto.key=list(space='top',title='l',cex=.4),
                   par.settings=list(superpose.symbol=list(col=c("black", "red", "green3", "blue","cyan", "magenta", "yellow", "gray"))))
print(ldaplot3d)
dev.off()







## Second approach 

Use several attributes of EVI and not the EFTs classification (after Domingo meeting). See Dionisio et al. 

```{r}

u <- evi %>% group_by(year) %>%
  mutate(q_evi_mean=ntile(evi_mean, 4),
         q_evi_cv=ntile(evi_cv, 4),
         n=n(), 
         jday=lubridate::yday(date_max)) %>%
  select(iv_malla_modi_id, year, q_evi_mean, q_evi_cv, n, date_max, jday) %>% 
  mutate(q_max = ifelse(jday > 81 & jday <= 173, 1,
                        ifelse(jday > 173 & jday <= 265, 2, 
                               ifelse(jday > 265 & jday <= 356, 3, 4))))  





Create raster

```{r}
library(sp)
x <- read.csv(file=paste(di, "/data/raw_iv.csv", sep= ""), header = TRUE, sep = ',')

aux <- x %>% 
  group_by(iv_malla_modi_id) %>%
  dplyr::select(iv_malla_modi_id, lng, lat, poblacion) 

df <- as.data.frame(dplyr::inner_join(aux, eft_final, by="iv_malla_modi_id"))


## definimos las coordenadas de los puntos
coordinates(df) <- ~lng+lat
## definimos el sistema de coordenadas WGS84
proj4string(df) <- CRS("+init=epsg:4326")

# Create empty raster
dd <- raster()
extent(dd) <- extent(df)
# Rasterize mq_evi_mean
evi_mean <- rasterize(df, dd, res=c(250,250), 'mq_evi_mean')
evi_cv <- rasterize(df, dd, 'mq_evi_cv')
evi_dmax <- rasterize(df, dd, 'mq_max')

xxx <- stack(evi_mean, evi_cv, evi_dmax)
plot(xxx)


library(rasterVis)
library(ggplot2)

pdf
gplot(evi_mean) +
    geom_raster(aes(fill = factor(value))) 

pdf(file=paste(di, '/evi_mean.pdf', sep=''), height = 8, width= 10)
gplot(evi_mean) +
  geom_raster(aes(fill = factor(value))) +
  scale_fill_manual(values=c('red','green', 'blue','black'),
                    'legend',labels = c("1", "2", "3", "4")) + 
  coord_equal() +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) 
dev.off()  





mq_evi_meanL


# df_puntos <- SpatialPoints(df[,c("lng", "lat")], df[,c("clu")])


## Ok a partir de aqui 

# Son las 1.27 de la mañana y estoy hasta los jjj
# Read centroid of all ndvi data 
pixel_all <- read.csv(file=paste(di, "/data/geoinfo/coordinates_iv_modis.csv", sep= ""), header = TRUE, sep = ',')
names(pixel_all) <- c("iv_malla_modi_id", "x", "y")
coordinates(pixel_all) <- ~x+y
proj4string(pixel_all) <- CRS("+init=epsg:4326")


# Create empty raster
r <- raster()
extent(r) <- extent(pixel_all)
# Rasterize
myr <- rasterize(pixel_all, r, 'z')




rr <- mask(myr, sn_ll)
plot(rr)























plot(myr)


# test
pixel_all$z <- 1


r <- rasterize(pixel_all, r, 'z')
plot(r)

projection(r)
extent(r) <- extent(pixel_all)
plot(r)



pixel_all

pixel_all <- SpatialPointsDataFrame(coords=pixel_all[, c("x","y")], data=pixel_all, 
                                    proj4string = CRS("+proj=utm +zone=30"))

head(pixel_all)


# with a SpatialPointsDataFrame
vals <- 1:n
p <- data.frame(xy, name=vals)
coordinates(p) <- ~x+y
r <- rasterize(p, r, '', fun=min)
#r2 <- rasterize(p, r, 'name', fun=max)
#plot(r, r2, cex=0.5)



r <- raster()

xx <- rasterize(pixel_all@data[c('x','y')], field=pixel_all@data[c('z')], r)

pixel_all$z <- 1
p <- pixel_all@data[c('x','y','z')]

ra <- rasterFromXYZ(p, res = c(250,250))

                                      C

proj4string=

# Set projection
pixel_all <- spTransform(pixel_all, CRS("+init=epsg:23030"))


## Read Sierra Nevada limits
enp <- rgdal::readOGR(dsn=paste(di, "/data/geoinfo/EENNPP/InfGeografica/InfVectorial/Shapes/ED50_30", sep=""),
                      layer = "EENNPP", verbose = FALSE)
# Subset limits of SN                      
sn <- subset(enp, NOMBRE == 'SIERRA NEVADA' & FIGURA == 'Espacio Natural')

# Retain only a field
sn <- sn[,c('FIGURA')]

# reproject naamp to lat/lon WGS84 ("geographic projection")
sn_ll <- spTransform(sn, CRS("+proj=longlat"))
sn_ll <- spTransform(sn_ll, CRS("+init=epsg:4326"))


# Extract (Overlay) point within sierranevada 
# https://cran.r-project.org/web/packages/sp/vignettes/over.pdf 
# pixel_sn <- pixel_all[!is.na(over(pixel_all,sn_ll)),]
pixel_sn <- pixel_all[complete.cases(over(pixel_all, sn_ll)), ] 
pixel_sn$a <- 1


ex <- as.data.frame(pixel_sn)[, c("x", "y", "a")]

gridded(pixel_all) <- TRUE
r <- raster()
library(raster)


f <- rasterize(ex, r)

head(pixel_sn)

pixel_all$a <- 1
head(pixel_all@data)

p <- pixel_all@data[,c('x','y','a')]


myr <- rasterFromXYZ(p)
r <- raster() 

myr <- rasterize(p, r)



coordinates(pix_all) <- ~x+y
xx <- points2grid(pixel_sn)

library(plotKML)
Rast2 <- vect2rast(pixel_all)

dd <- spDists(pixel_all)







0.678661
points <- SpatialPoints(s100_ras[,c('x','y')], s100_ras[,c('z')]
pixels <- SpatialPixelsDataFrame(points, tolerance = 0.916421, points@data)
raster <- raster(pixels[,'z'])





library(maptools)
coordinates(df) <- ~lng+lat
xx <- points2grid(df)


library(sp)
library(plotKML)

# Create spatial point dataframe 
dfsp <- SpatialPointsDataFrame(coords = df[,c("lng", "lat")],
                               data=df)
plot(dfsp)

# Convert into 
pixels <- SpatialPixelsDataFrame(dfsp, tolerance = 0.0678661, dfsp@data)

r <- raster(pixels[,"clu"])
plot(r)

head(pixels)

vect2rast(df)


delmepol <- as(delmepx,"SpatialPolygonsDataFrame")
> delmepx2 <- SpatialPixelsDataFrame(coordinates(delmepol), delmepol at data)
> suggested tolerance minimum: 0.000635728


df <- as(df, "SpatialGridDataFrame")


points <- SpatialPoints(s100_ras[,c('x','y')], s100_ras[,c('z')]
pixels <- SpatialPixelsDataFrame(points, tolerance = 0.916421, points@data)
raster <- raster(pixels[,'z'])






df <- SpatialPixelsDataFrame(coordinates())

grd.pts = SpatialPixels(SpatialPoints(df))


auxr <- df [, c("lat", "lng", "clu")]
names(auxr) <- 

myr <-rasterFromXYZ(auxr)

# Create empty raster
r <- raster() 

# Specify function 
extent(r) <- extent(dfsp)
myr <- rasterize(dfsp, r, "clu", fun='first')



# VAS POR AQUI CANTINFLAS 
library(raster)

```

